{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-08 Paper_ttbarH_Draft.tex
Small edits in the conclusions

The
results shown in Tables \ref{table11} and \ref{table12} reveal that
with $5\times 10^3$ and $1\times 10^4$ events, respectively, the
observables $\mathcal{A}(\epsilon_4)$ and $\mathcal{A}(\epsilon_{10})$
are still useful for testing $\kpt$. Without taking into account
the loss of events that would take place in a realistic 
experimental analysis, these numbers of events
correspond to a luminosity of $\sim
300\,$-$\,600\,\mathrm{fb}^{-1}$ for the SM and even smaller for the
$\mathrm{CP}$-mixed cases (due to their larger cross section). This range
of luminosities is in principle achievable in the short term by the
LHC. We note that in order to be fully conclusive about the required
luminosity, it is important to include the effects of hadronization,
detector resolution, reconstruction efficiencies and so
forth. Such an analysis, however, is beyond the scope of this
paper.
%%%%%%%%%%%% with Cuts
%51.46/17 -0.02 +- 0.08
%45.48/17  -1.09 +- 0.07
%65.60/17   0.96 +- 0.08
%28.84/17   0.02 +- 0.07
%%%%%%%
%9.13/17     0.01 +- 0.06
%9.05/17     -0.98 +- 0.07
%19.7/17     0.80 +- 0.07
%16.59/17    0.06 +- 0.07
%
%%%%%%%%%%%% without Cuts
%16.36/17    0.0022 +-0.06
%15.25/17    -0.82 +- 0.07
%12.80/17    0.81 +- 0.07
%19.38/17    0.11 +- 0.08
%%%%%%
%7.45/17    0.005 +- 0.06
%18.17/17   -0.77 +- 0.07
%9.59/17    0.73 +- 0.06
%12.39/17   0.09 +- 0.08
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec7}
%
In this paper we have presented a collection of $\mathrm{CP}$-odd
observables based on triple product correlations
in $\ppprocess$ that are useful for
disentangling the relative sign between the scalar ($\kp$) and a
potential pseudoscalar ($\kpt$) top-Higgs couplings.
We have tested the
sensitivity of the various triple product correlations
{\bf (KK: OK? ``observables'' was repeated)}
by considering three types of
observables: asymmetries, angular distributions, and mean values.
Using these observables, we have examined several benchmark
scenarios, focusing in particular on the SM ($\kp=1$ and $\kpt=0$)
and on two ``$\mathrm{CP}$-mixed'' scenarios ($\kp=1$ and $\kpt=\pm1$).
\par

@@

We have also proposed a combination of the TPs,
$\epsilon_4\equiv \epsilon_3-\epsilon_2$,
which has a greater sensitivity than $\epsilon_1$-$\epsilon_3$.
With $1\times 10^5$ events, for example, the asymmetry associated
with this TP gives an effective separation 
between the $\mathrm{CP}$-mixed scenarios that
exceeds those coming from $\epsilon_1$-$\epsilon_3$
by at least $3\sigma$.  {\bf (KK: please check my rewording for accuracy.)}
When a similar
combination is constructed by using the leptons' momenta instead of the
spin vectors ($\epsilon_8$), the sensitivity in the asymmetry is
decreased by $\sim 3\sigma$ compared to the asymmetry associated
with $\epsilon_4$ for
the same number of events, giving values compatible with those
obtained for the asymmetries of $\epsilon_2$ and $\epsilon_3$. \par

@@

Finally, we have discussed the experimental {\bf (KK: OK?)}
feasibility of the most sensitive
observables proposed here. We have found that with $5\times 10^3$ and
$1\times 10^4$ events, respectively, the asymmetries
associated with $\epsilon_4$ and $\epsilon_{10}$ are still
useful for testing the hypotheses $(\kp=1,\kpt=\pm 1)$, giving rise to
separations of order $\sim 6\sigma$. These numbers of events
are within reach in the short term at the LHC,
so that these observables could in principle be used
to test the sign of $\kpt/\kp$ within that context.
{\bf (KK: maybe reword this sentence a bit\ldots?)}

>>>>

The
results shown in Tables \ref{table11} and \ref{table12} reveal that
with $5\times 10^3$ and $1\times 10^4$ events, respectively, the
observables $\mathcal{A}(\epsilon_4)$ and $\mathcal{A}(\epsilon_{10})$
are still useful for testing $\kpt$. Without taking into account
the loss of events that would take place in a realistic 
experimental analysis, these numbers of events
correspond to a luminosity of $\sim
300\,$-$\,600\,\mathrm{fb}^{-1}$ for the SM and even smaller for the
$\mathrm{CP}$-mixed cases (due to their larger cross section). This range
of luminosities is in principle achievable in the short term by the
LHC. We note that in order to be fully conclusive about the required
luminosity, it is important to include the effects of hadronization,
detector resolution, reconstruction efficiencies and so
forth. Such an analysis, however, is beyond the scope of this
paper.
%%%%%%%%%%%% with Cuts
%51.46/17 -0.02 +- 0.08
%45.48/17  -1.09 +- 0.07
%65.60/17   0.96 +- 0.08
%28.84/17   0.02 +- 0.07
%%%%%%%
%9.13/17     0.01 +- 0.06
%9.05/17     -0.98 +- 0.07
%19.7/17     0.80 +- 0.07
%16.59/17    0.06 +- 0.07
%
%%%%%%%%%%%% without Cuts
%16.36/17    0.0022 +-0.06
%15.25/17    -0.82 +- 0.07
%12.80/17    0.81 +- 0.07
%19.38/17    0.11 +- 0.08
%%%%%%
%7.45/17    0.005 +- 0.06
%18.17/17   -0.77 +- 0.07
%9.59/17    0.73 +- 0.06
%12.39/17   0.09 +- 0.08
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec7}
%
In this paper we have presented a collection of $\mathrm{CP}$-odd
observables based on triple product correlations
in $\ppprocess$ that are useful for
disentangling the relative sign between the scalar ($\kp$) and a
potential pseudoscalar ($\kpt$) top-Higgs couplings.
We have tested the
sensitivity of the various triple product correlations
by considering three types of
observables: asymmetries, angular distributions, and mean values.
Using these observables, we have examined several benchmark
scenarios, focusing in particular on the SM ($\kp=1$ and $\kpt=0$)
and on two ``$\mathrm{CP}$-mixed'' scenarios ($\kp=1$ and $\kpt=\pm1$).
\par

@@

We have also proposed a combination of the TPs,
$\epsilon_4\equiv \epsilon_3-\epsilon_2$,
which has a greater sensitivity than $\epsilon_1$-$\epsilon_3$.
With $1\times 10^5$ events, for example, the asymmetry associated
with this TP gives an effective separation 
between the $\mathrm{CP}$-mixed scenarios that
exceeds those coming from $\epsilon_1$-$\epsilon_3$
by at least $3\sigma$.  
When a similar
combination is constructed by using the leptons' momenta instead of the
spin vectors ($\epsilon_8$), the sensitivity in the asymmetry is
decreased by $\sim 3\sigma$ compared to the asymmetry associated
with $\epsilon_4$ for
the same number of events, giving values compatible with those
obtained for the asymmetries of $\epsilon_2$ and $\epsilon_3$. \par

@@

Finally, we have discussed the experimental 
feasibility of the most sensitive
observables proposed here. We have found that with $5\times 10^3$ and
$1\times 10^4$ events, respectively, the asymmetries
associated with $\epsilon_4$ and $\epsilon_{10}$ are still
useful for testing the hypotheses $(\kp=1,\kpt=\pm 1)$, giving rise to
separations of order $\sim 6\sigma$. These numbers of events
are within reach in the short term at the LHC,
so that these observables could in principle be used
to test the sign of $\kpt/\kp$ within that context.
{\bf (KK: maybe reword this sentence a bit\ldots?)}
